Modal type theory based on the intuitionistic epistemic logic

### 2018-01-19 article.tex
added rewritten lemma

@@

>>>>

It is clearly that these lemmas could be extended for IEL$^{-}$ with $\vee$ and $\neg$ similary.

@@

\begin{lemma} Generation lemma.

  i) Let $\Gamma \vdash {\bf pure \:} M : {\bf K}A$, then $\Gamma \vdash M : A$;

  ii) Let $\Gamma \vdash {\bf let \: pure \:} \vec{x} = \vec{M} {\: \bf in \:} N : {\bf K}B$, there are some $A_1,\dots,A_n \in \mathbb{T}_{{\bf K}}$,
  such that $\Gamma \vdash \vec{M} : {\bf K} \vec{A}$ and $\vec{x} : \vec{A} \vdash N : B$.
\end{lemma}

  Induction on $\Gamma \vdash {\bf pure \:} M : {\bf K}A$ and $\Gamma \vdash {\bf let \: pure \:} \vec{x} = \vec{N} {\: \bf in \:} N : {\bf K}B$ correspondently.
\end{proof}

\begin{lemma} Weakening.

  Let $\Gamma \vdash M : A$ and $\Gamma \subseteq \Delta$, then $\Delta \vdash M : A$.

  1) Let $\Gamma, x : A \vdash x : A$ and $\Gamma \subseteq \Delta$, then $\Delta, x : A \vdash x : A$ trivially.

  2) Let $\Gamma \vdash {\bf pure \:} M : {\bf K}A$. Then $\Gamma \vdash M : A$ by generation and $\Delta \vdash M : A$ by assumption. So $\Delta \vdash {\bf pure \:} M : {\bf K} A$ by ${\bf K}_I$.

  3) Let $\Gamma \vdash {\bf let \: pure \:} \vec{x} = \vec{M} {\: \bf in \:} N : {\bf K}B$ and $\Gamma \subseteq \Delta$. Then $\Gamma \vdash \vec{M} : {\bf K}\vec{A}$ and $\vec{x} : \vec{A} \vdash N : B$.

  By assumption $\Delta \vdash \vec{M} : {\bf K}\vec{A}$. So $\Delta \vdash {\bf let \: pure \:} \vec{x} = \vec{N} {\: \bf in \:} N : {\bf K}B$ by $\text{let}_{{\bf K}}$.
\end{proof}

\begin{defin} Type substituition

  The substituition of type $C$ for type variable $B$ in type $A$ inductively defined as follows:

  1) $B [B := C] = B$ and $D [B := C] = D$, if $B \neq D$;

  2) $(A_1 \alpha A_2)[B := C] = (A_1[B := C]) \alpha (A_2[B := C])$, where $\alpha \in \{ \to, \times \}$;

  3) $({\bf K}A)[B := C] = {\bf K}(A [B := C])$.

  4) Let $\Gamma$ be the context, then $\Gamma [B := C] = \{ x : (A[B := C]) \: | \: x : A \in \Gamma \}$
\end{defin}

\begin{lemma} Substituition lemma.

    i) Let $\Gamma, x : A \vdash M : B$ and $\Gamma \vdash N : A$, then $\Gamma \vdash M [x := N] : B$.

    ii) Let $\Gamma \vdash M : A$, then $\Gamma [B := C] \vdash M : (A [B := C])$.

i) For term substitution:

1) Let $\Gamma, x : A \vdash x : A$ and $\Gamma \vdash N : A$, but $x [x := N] = N$, so $\Gamma \vdash N : A$.

2) Let $\Gamma, x : A \vdash {\bf pure \:} M : {\bf K}B$ and $\Gamma \vdash N : A$.

By generation $\Gamma, x : A \vdash M : B$ and by assumption $\Gamma \vdash M [x := N] : B$.

By $K_I$, $\Gamma \vdash {\bf pure \:} (M [x := N]) : {\bf K}B$.

3) Let $\Gamma, y : A \vdash {\bf let \: pure \:} \vec{x} = \vec{M} {\: \bf in \:} N : {\bf K} B$ and $\Gamma \vdash N : A$.

By generation, $\Gamma, y : A \vdash \vec{M} : {\bf K} \vec{A}$ and $\vec{x} : \vec{A} \vdash N : B$.

By hypothesis, $\Gamma \vdash \vec{M}[x := N] : {\bf K} \vec{A}$.

Hence $\Gamma \vdash {\bf let \: pure \:} \vec{x} = \vec{M}[x := N] {\: \bf in \:} N : {\bf K} B$.

ii) For type substitution

1) Let $\Gamma, x : A \vdash x : A$, so $\Gamma [A := C], x : (A[A := C]) \vdash x : (A[A := C])$, or

$\Gamma [A := C], x : C \vdash x : C$.

2) Let $\Gamma \vdash {\bf pure \:} M : {\bf K}A$. By generation $\Gamma \vdash M : A$ and by assumption $\Gamma [B := C] \vdash M : A[B := C]$.

By $K_I$ $\Gamma \vdash {\bf pure \:L} M : {\bf K}(A[B := C])$.

3) $\Gamma \vdash {\bf let \: pure \:} \vec{x} = \vec{M} {\: \bf in \:} N : {\bf K}B$. By generation $\Gamma \vdash \vec{M} : {\bf K}\vec{A}$ and $\vec{x} : \vec{A} \vdash N : B$.

By assumption $\Gamma [B_1 := C] \vdash \vec{M} : {\bf }{K}\vec{A}[B_1 := C]$ and $\vec{x} : \vec{A}[B_1 := C] \vdash N : B[B_1 := C]$.

So by $\text{let}_{{\bf K}}$, $\Gamma [B_1 := C] \vdash {\bf let \: pure \:} \vec{x} = \vec{M} {\: \bf in \:} N : {\bf K}(B[B_1 := C])$.

\begin{theorem} Subject reduction
\end{theorem}
